---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# invasiongraph

<!-- badges: start -->
[![R-CMD-check](https://github.com/DICELab-NCSU/invasiongraph/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/DICELab-NCSU/invasiongraph/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `invasiongraph` is to compute the potential community assembly pathways for a community of interacting species. The core functions in this package come from the R code archive that accompanies:

> Hofbauer, J., Schreiber, S.J. (2022) Permanence via invasion graphs: incorporating community assembly into modern coexistence theory. J. Math. Biol. 85:54. [https://doi.org/10.1007/s00285-022-01815-2](https://doi.org/10.1007/s00285-022-01815-2)

In addition to the more accessible format of an R package, we have added:

- Checks and informative error messages
- Grammar of Graphics plotting via `tidygraph` and `ggraph`
- (planned) Dedicated object classes
- (planned) Support for uncertainty propagation

## Installation

You can install the development version of `invasiongraph` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("DICELab-NCSU/invasiongraph")
```

## Core functionality

### Simulate data for a Lotka-Volterra competitive system
```{r lv}
library(invasiongraph)

# simulate Lotka-Volterra system
set.seed(2332)
n <- 6  # number of species
A <- -diag(n) - 1.5 * matrix(runif(n^2), n, n)  # interaction matrix
r <- matrix(1, n, 1)  # intrinsic growth rates
```

### Calculate invasion schemes and graphs
```{r calc}
# compute the invasion scheme
sch <- inv_scheme(A, r)

# calculate the invasion graph
gra <- inv_graph(IS = sch)
```

### Visualize invasion graphs
```{r plot}
# tidy invasion graph to prepare for plotting
tidy_gra <- tidy_inv_graph(gra)

# plot
ggIG(tidy_gra, node_size = 8, edge_width = c(0.05, 0.2))
```

### Propagating uncertainty

### Distinguishing invasion graphs
The edges that differentiate candidate invasion graphs may be easily identified for a small number of candidates for a pool with low species richness. This task quickly becomes unfeasible as the number of candidate invasion graphs or the size of the species pool grows.
```{r distinct}
# generate candidate invasion graphs for the same species pool
set.seed(9823)
n <- 3  # set number of species
As <- replicate(5, -diag(n) - 1.5 * matrix(runif(n^2), n, n), simplify = FALSE)
r <- matrix(1, n, 1)
schs <- lapply(As, inv_scheme, r)
gras <- lapply(schs, inv_graph)

# homogenize the nodes across a set of candidate invasion graphs
(pgras <- pad_adj_mats(gras))

# prepare a binary character matrix for the presence of edges
adj2char(pgras)

# cluster candidate invasion graphs, determine the edges that
# distinguish clusters
# TODO

```
